Commit Rater

### 2015-08-24 presentations/paper/methodology.tex
Spell check data synthesis

% TODO: Put special focus on those Natural Language Processing
% TODO: Maybe mention, that our synthesis contains actions that may have belonged into extraction, but we found the terms more fitting to our implementation

@@

Almost all of the criteria below relate to the commit message. Only one of them states a very superficial rule about the changes in the commit. None of them process the code itself, neither inside the changes nor in the the code-base before or after applying the commit, as such criteria would require very language-specific knowledge that would have to be manually implemented for each desired language. By keeping our criteria language-independent, they remain appliccable to all Git Repositories.

In general, commit messages should consist of a subject line and a body \cite{OffGuide}. \cite{CB} summarizes the most important guidelines very nicely, and the first seven criteria below are directly taken or inspired from the blog post. Note that the seventh mentioned rule could not be made into a criterion, since it would require actual understanding of the commit message. Omitting this rule, we still infered one additional criterium (\ref{subs:body_used}).

@@

% TODO: List all criteria with details

@@

Additionally, large subject lines might hint at having done more than one thing in a commit, since the author needs more space to explain what the commit does. Logically separating changesets is another rule from \cite{OffGuide}, which of course cannot be evaluated without much language-specific effort.

\subsubsection{capitalize\_subject}
\label{subs:capitalize_subject}
The first letter of the subject line should be capitalized. Although it could be argued that this is more of a convention, subject lines should be complete sentences, and sentences in the english language start with a capital letter. This rule is only mentioned by \cite{CB}. It may not be as important as other rules, but fullfilling it requires little effort and makes reading the message a nicer.

\subsubsection{no\_period\_subject}
\label{subs:no_period_subject}
The subject line should have no trailing period. It servers no purpose, since the body of a commit message should be separated by a blank line (see \ref{empty_second_line}) and omitting it helps with the 50 character limit. Again, the only explicit mention of this rule is \cite{CB}, although the Git manual \cite{OffGuide} and Linus Torvalds \cite{SR} both seem to agree on this.

\subsubsection{imperative\_subject}
\label{subs:imperative_subject}
The subject line should be written in imperative present, e.g. ``Add a function that...'' (as mentioned in \cite{OffGuide}). There are a lot of opinions on this rule and many authors seem to prefer regular present tense (e.g. ``Adds a function that...'') or past tense (e.g. ``Added a function that...''), which both have their own justification. The most important reason to use the imperative is consistency with git itself, which usually generates messages this way, the most prominent example being messages of automatic merges (e.g. ``Merge branch \'master\' of https://github.com/hartenfels/Commit-Rater''). \cite{CB} gives a very nice explanation on how to write messages in the imperative.

This criterion requires natural language processing of the commit
message. For this purpose we use a perl module \footnote{http://search.cpan.org/dist/Lingua-EN-Tagger/Tagger.pm} and use it to get a list of the forms of the words in the subject line. If the list contains a verb in base present form, the criterion is passed. This is of course a very heuristic approach, but it successfully fails regular present tense or past tense subjet lines and furthermore ensures that there is a verb, so that nonsense messages like ``Some changes'' are failed too.

\subsubsection{body\_used}
\label{subs:body_used}
Additionally to the subject line, there should be a body that further explains what the commit does and why it does what it does (\cite{OffGuide}). The body consists of multiple lines and multiple paragraphs can be used, separated by blank lines. It is also acceptable to use bullet points. This criterion only checks if there is a body.

@@

\subsubsection{empty\_second\_line}
\label{subs:empty_second_line}
The subject line and the body should be separated by an empty line (\cite{TP}). This is how programs (including git itself) parsing the commit message which part is the subject line and which the body, so if a body is used, meeting this criterion is crucial. If no body is used, the test on this criterion will be undefined.

@@

\subsubsection{no\_long\_message}
\label{subs:no_long_message}
The subject line should be limited to less than 10 words. This is an extension of the subject\_limit criterion in \ref{subject_limit}, which might rarely allow 10 or more words. The reasoning behind this criterion again is, that many words hint at more than one logical changeset in one commit. Also, concision should help making a message more easily understandable and scanning a log for a particular commit takes less time. If there is need for longer explanations, the body should be used.

@@

\subsubsection{no\_bulk\_change}
\label{subs:no_bulk_change}
Large changesets hint at a commit with more than one logical changeset.  If 10 or more files are changed by a commit, chances are that that commit should have been separated multiple commits. Furthermore, even a commit with 10 or more changes only contains one logical changeset, this hints at bad software architecture, altough this should maybe not be reflected in the evaluation of commits.

@@

\subsubsection{no\_vulgarity}
\label{subs:no_vulgarity}
A commit message should obviously not contain any vulgarity for many reasons, but it should suffice to say that such things are unprofessional and will rarely make the commit any better.

Checking for vulgarity is done with a perl module \footnote{http://search.cpan.org/~abigail/Regexp-Common-2013031301/lib/Regexp/Common/profanity.pm} that contains a list of offensive words. The test for the criterion is passed if none of the words are found in the commit message.

This criterion may or may not have been inspired by \url{http://www.commitlogsfromlastnight.com/}

\subsubsection{no\_misspelling}
\label{subs:no_misspelling}
Of course, spelling is important. Correct or at least consistant spelling makes commit messages easier to read and scan, and makes them searchable.

This criterion is hugely proplematic. In principle, spell checking is easily done with one of many libraries \footnote{We use http://search.cpan.org/~hank/Text-Aspell/Aspell.pm}, but such libraries will report technical terms as errors and since we cannot manually whitelist all of those, we need to allow a certain number of ``errors'' per message, which we have set to less than 2. This will of course sometimes hide real errors. Maybe further research could provide an adequate solution to this problem or at least analyse the precision of applying a standard spell checker to very domain specific texts.

>>>>

% TODO: Maybe mention, that our synthesis contains actions that may have belonged into extraction, but we found the terms more fitting to our implementation

@@

Almost all of the criteria below relate to the commit message. Only one of them states a very superficial rule about the changes in the commit. None of them process the code itself, neither inside the changes nor in the the code-base before or after applying the commit, as such criteria would require very language-specific knowledge that would have to be manually implemented for each desired language. By keeping our criteria language-independent, they remain appliccable to all Git repositories.

In general, commit messages should consist of a subject line and a body \footnote{See \cite{OffGuide} for an exhaustive explanation and an example}. \cite{CB} summarizes the most important guidelines very nicely, and the first seven criteria below are directly taken or inspired from the blog post. Note that the seventh mentioned rule could not be made into a criterion, since it would require actual understanding of the commit message. Omitting this rule, we still infered one additional criterium (\ref{subs:body_used}) that we found missing in the list.

@@

@@

Additionally, large subject lines might hint at having done more than one thing in a commit, since the author needs more space to explain what the commit does. Logically separating changesets is another rule from \cite{OffGuide}, which of course cannot be evaluated without great language-specific effort.

\subsubsection{capitalize\_subject}
\label{subs:capitalize_subject}
The first letter of the subject line should be capitalized. Although it could be argued that this is more of a convention, subject lines should be complete sentences, and sentences in the english language start with a capital letter. This rule is only mentioned by \cite{CB}. It may not be as important as other rules, but fulfilling it requires little effort and makes reading the message nicer.

\subsubsection{no\_period\_subject}
\label{subs:no_period_subject}
The subject line should have no trailing period. It servers no purpose, since the body of a commit message should be separated by a blank line (see \ref{empty_second_line}) and omitting it helps with the 50 character limit. Again, the only explicit mention of this rule is \cite{CB}, although the Git manual \cite{OffGuide} and Linus Torvalds \cite{SR} both seem to adhere to it.

\subsubsection{imperative\_subject}
\label{subs:imperative_subject}
The subject line should be written in imperative present tense, e.g. ``Add a function that...'' (as mentioned in \cite{OffGuide}). There are a lot of opinions on this rule and some authors seem to prefer regular present tense (e.g. ``Adds a function that...'') or past tense (e.g. ``Added a function that...''), which both have their own justification. In the authors opinion, the most important reason to use the imperative is consistency with git itself, which usually generates messages this way, the most prominent example being messages of automatic merges (e.g. ``Merge branch \'master\' of https://github.com/hartenfels/Commit-Rater''). \cite{CB} gives very nice instructions on how and why to write messages in the imperative.

This criterion requires natural language processing of the commit
message. For this purpose we use a Perl module \footnote{http://search.cpan.org/dist/Lingua-EN-Tagger/Tagger.pm} and use it to get a list of the forms of the words in the subject line. If the list contains a verb in base present form, the criterion is passed. This is of course a very heuristic approach, but it successfully fails regular present tense or past tense subjet lines and furthermore ensures that there is a verb, so that nonsense messages like ``Some changes'' are failed too.

\subsubsection{body\_used}
\label{subs:body_used}
In addition to the subject line, there should be a body that further explains what the commit does and why it does what it does (\cite{OffGuide}). The body consists of multiple lines and multiple paragraphs can be used, separated by blank lines. It is also acceptable to use bullet points. This criterion only checks if there is a body.

As the Git manual \cite{OffGuide} and Linus Torvalds \cite{SR} seem to disagree on this, we decided to make the useage of the body mandatory.

@@

\subsubsection{empty\_second\_line}
\label{subs:empty_second_line}
The subject line and the body should be separated by an empty line (\cite{TP}). This is how programs (including git itself) parsing the commit message know, which part is the subject line and which the body, so if a body is used, meeting this criterion is crucial. If no body is used, the test on this criterion will be undefined.

@@

\subsubsection{no\_long\_message}
\label{subs:no_long_message}
The subject line should be limited to less than 10 words. This is an extension of the subject\_limit criterion in \ref{subject_limit}, which might rarely allow 10 or more words. The reasoning behind this criterion is agein, that many words hint at more than one logical changeset in one commit. Also, concision should help making a message more easily understandable and scanning a log for a particular commit takes less effort. If there is need for longer explanations, they should be moved to the body.

@@

\subsubsection{no\_bulk\_change}
\label{subs:no_bulk_change}
Large changesets hint at a commit with more than one logical changeset. If 10 or more files are changed by a commit, chances are that that commit should have been divided into multiple commits. Furthermore, even a commit with 10 or more changes only contains one logical changeset, this hints at bad software architecture, altough this should maybe not be reflected in the evaluation of commits.

@@

\subsubsection{no\_vulgarity}
\footnote{This criterion may or may not have been inspired by \url{http://www.commitlogsfromlastnight.com/}}
\label{subs:no_vulgarity}
A commit message should obviously not contain any vulgarity for many reasons, but it should suffice to say that such things are unprofessional and will rarely make the commit any better.

Checking for vulgarity is done with a Perl module \footnote{http://search.cpan.org/~abigail/Regexp-Common-2013031301/lib/Regexp/Common/profanity.pm} that contains a list of offensive words. The test for the criterion is passed if none of the words are found in the commit message.

\subsubsection{no\_misspelling}
\label{subs:no_misspelling}
Of course, spelling is important. Correct or at least consistent spelling makes commit messages easier to read and scan, and makes them searchable.

This criterion is hugely problematic. In principle, spell checking is easily done with one of many libraries \footnote{We use http://search.cpan.org/~hank/Text-Aspell/Aspell.pm}, but such libraries will report technical terms as errors and since we cannot manualy whitelist all of those, we need to allow a certain number of ``errors'' per message, which we have set to 2. This will of course sometimes hide real errors. Maybe further research could provide an adequate solution to this problem or at least analyse the precision of applying a standard spell checker to very domain specific texts.
